### 2024-02-28 presentation/parts/introduction.tex
WIP

\begin{frame}
    % Background on Corti and the problem of medical communication, diagnosis, and documentation.
    \frametitle{Background}
    \begin{columns}
        \begin{column}{0.6\textwidth}
            FILL ME OUT. \\
            Background on Corti, motivation for project.
        \end{column}
        \begin{column}{0.4\textwidth}
        \end{column}
    \end{columns}
\end{frame}

@@

\begin{frame}[t]
    \frametitle{Medical dialogue}
    \begin{columns}[t]
        \begin{column}{0.4\textwidth}
            \begin{itemize}
                \item <2> General practitioner
                \item <2> Nurse
                \item <2> Midwife
                \item <2> Emergency medical dispatcher
                \item <2> Paramedic
                \item <2> Emergency room
                \item <2> Health insurance
            \end{itemize}
        \end{column}
        \begin{column}{0.6\textwidth}
            \begin{figure}
                \centering
                \includegraphics[width=0.9\textwidth]{figures/corti_sketch_conversations.png}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{columns}
        \begin{column}{0.35\textwidth}
            \begin{itemize}
                \item <1-> \highlight{Assist} with documentation.
                \item <1-> \highlight{Augment} communication.
                \item <1-> \highlight{Improve} decision-making.
                \vspace{1em}
                \item <2-> \highlight{Reduce} number of impact of medical errors and adverse events.
                \item <2-> \highlight{Free up} time spent on documentation for patient care.
            \end{itemize}
        \end{column}
        \begin{column}{0.65\textwidth}
            \centering
            \includegraphics[width=0.95\textwidth]{figures/corti_sketch_office.png}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning systems}
    \begin{itemize}
        \item <1-> \highlight{Data}: Quality, quantity, diversity, bias, privacy, ethics.
        \item <2-> \highlight{Task}: Context, domain, language, culture, purpose.
        \vspace{1em}
        \item <3-> \highlight{Interpretability} of how a model works (transparency, accountability, regulation).
        \item <4-> \highlight{Explainability} of model predictions (trust, understanding, feedback).
        \item <5-> \highlight{Fairness} in treatment of different groups of people.
        \item <6-> \highlight{Robustness} to noise, outliers, adversarial attacks, and distribution shift.
    \end{itemize}
\end{frame}

>>>>

@@

\begin{frame}[t]
    \frametitle{Medical dialogue}
    \begin{columns}[t]
        \begin{column}{0.4\textwidth}
            \begin{itemize}
                \item <2> General practitioner
                \item <2> Nurse
                \item <2> Midwife
                \item <2> Emergency medical dispatcher
                \item <2> Paramedic
                \item <2> Emergency room
                \item <2> Health insurance
            \end{itemize}
        \end{column}
        \begin{column}{0.6\textwidth}
            \vspace{-2em}
            \begin{figure}[t]
                \centering
                \includegraphics[width=0.9\textwidth]{figures/corti_sketch_conversations.png}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{columns}
        \begin{column}{0.35\textwidth}
            \begin{itemize}
                \item <1-> \highlight{Assist} with documentation.
                \item <1-> \highlight{Augment} communication.
                \item <1-> \highlight{Improve} decision-making.
                \vspace{1em}
                \item <2-> \highlight{Reduce} the impact of medical errors and adverse events.
                \item <2-> \highlight{Free up} time spent on documentation for patient care.
            \end{itemize}
        \end{column}
        \begin{column}{0.65\textwidth}
            \centering
            \includegraphics[width=0.95\textwidth]{figures/corti_sketch_office.png}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning systems}
    \begin{itemize}
        \item <1-> \highlight{Data}: Quality, quantity, diversity, bias, privacy, ethics.
        \item <2-> \highlight{Task}: Context, domain, language, culture, purpose.
        \vspace{1em}
        \item <3-> \highlight{Interpretability} of how a model works (transparency, accountability, regulation).
        \item <4-> \highlight{Explainability} of model predictions (trust, understanding, feedback).
        \item <5-> \highlight{Fairness} in treatment of different groups of people.
        \item <6-> \highlight{Robustness} to noise, outliers, distribution shift, and adversarial attacks.
    \end{itemize}
\end{frame}
